---
title: "Climate Action Analyses"
author: Fabian Dablander
date: "`r format(Sys.time(), '%d %B, %Y')`"
header-includes:
   - "\\usepackage{booktabs}"
output:
  html_document:
    toc: true
    theme: united
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  echo = TRUE, warning = FALSE, message = FALSE, eval = TRUE, cache = FALSE,
  fig.align = 'center', fig.width = 10, fig.height = 12, dpi = 300,
  out.width='100%', out.height='100%'
)
```

<!-- avoid border around images -->
<style>
    img {
        border: 0;
    }
</style>

# Setup
This document runs the statistical analyses reported in the paper Dablander, F., Sachisthal, M., & Haslbeck, J.M.B. (accepted). Climate Actions by Climate and Non-Climate Researchers. *npj Climate Action*.

```{r}
library(brms)
library(caret)
library(knitr)
library(dplyr)
library(scales)
library(ggplot2)
library(forcats)
library(corrplot)
library(latex2exp)
library(BayesFactor)
library(tidyverse)
library(qualtRics)
library(kableExtra)
library(RColorBrewer)
source('../helpers.R')

ptheme <- theme(
  plot.title = element_text(hjust = .5),
  text = element_text(size = 14),
  legend.key = element_blank(),
  panel.background = element_blank(),
  legend.position = 'none',
  axis.line.x = element_line(),
  axis.line.y = element_line(),
  strip.background = element_blank()
)
ptheme2 <- ptheme + theme(legend.position = 'bottom')
```

# Data preparation
We load the data and create variables and categorizations that are useful for the subsequent analyses.

```{r}
dat_final <- readRDS('../data/DataS3_Final.RDS') %>% 
  mutate(
    engaged_protest = as.numeric(BehLegal == 2),
    engaged_advocacy = as.numeric(Beh_EngPub == 2),
    research_fact = factor(
      Research_std,
      labels = c("Not at all", "Very little", "A moderate amount", "Quite a bit", "A great deal")
    )
  )

dat_num <- readRDS('../data/DataS1_Anonymized.RDS') %>% 
  mutate(
    # Natural science as reference category
    humanities = as.numeric(
      Field == 1 | open_field == "Humanities (e.g., History, Languages, Law)"
    ),
    social_science = as.numeric(
      Field == 2 | open_field == "Social and behavioural sciences (e.g., Economics, Sociology, Psychology)"
    ),
    formal_science = as.numeric(
      Field == 4 | open_field == "Formal sciences (e.g., Computer science, Logic, Mathematics)"
    ),
    applied_science = as.numeric(
      Field == 5 | open_field == "Professions and applied sciences (e.g., Agriculture, Engineering)"
    ),
    medical_science = as.numeric(open_field == "Medical sciences"),
    other_science = as.numeric(open_field == "Other, please specify:"),
    
    fieldname = case_when(
      humanities == 1 ~ 'Humanities',
      social_science == 1 ~ 'Social and behavioural sciences',
      formal_science == 1 ~ 'Formal sciences',
      applied_science == 1 ~ 'Professions and applied sciences',
      medical_science == 1 ~ 'Medical sciences',
      other_science == 1 ~ 'Other',
      TRUE ~ 'Natural sciences'
    ),
    
    position_name = case_when(
      Position == 1 ~ 'PhD candidate',
      Position == 2 ~ 'Postdoc',
      Position == 3 ~ 'Assisstant professor',
      Position == 4 ~ 'Associate professor',
      Position == 5 ~ 'Full professor',
      TRUE ~ 'Other'
    ),
    
    reduced_car = as.numeric(Beh_incNotApp_1 == 2),
    electric_vehicle = as.numeric(Beh_incNotApp_2 == 2),
    energy_home = as.numeric(Beh_incNotApp_3 == 2),
    fewer_children = as.numeric(Beh_incNotApp_4 == 2),
    talk_climate = as.numeric(Beh_incNotApp_5 == 2),
    donate_money = as.numeric(Beh_incNotApp_6 == 2),
    veggie_diet = as.numeric(Beh_incNotApp_7 == 2),
    reduced_flying = as.numeric(Beh_incNotApp_8 == 2),
    
    signed_petitions = as.numeric(Beh_others_1 == 2),
    advocated_change = as.numeric(Beh_others_2 == 2),
    engaged_policymakers = as.numeric(Beh_others_3 == 2),
    wrote_letters = as.numeric(Beh_others_4 == 2),
    engaged_disobedience = as.numeric(Beh_others_7 == 2),
    engaged_protest = as.numeric(BehLegal == 2),
    engaged_advocacy = as.numeric(Beh_EngPub == 2)
  )
    
dat_final$position <- factor(
  dat_num$position_name,
  levels = c(
    'Full professor', 'Associate professor', 'Assisstant professor',
    'Postdoc', 'PhD candidate', 'Other'
  )
)

dat_final$fieldname <- dat_num$fieldname
dat_final$field <- factor(
  dat_num$fieldname,
  levels = c(
    'Natural sciences', 'Social and behavioural sciences', 'Medical sciences',
    'Formal sciences', 'Humanities', 'Professions and applied sciences', 'Other'
  )
)

dat_final$country <- ifelse(is.na(dat_num$Country), 'not specified', dat_num$Country)
dat_final$continent <- ifelse(is.na(dat_num$Continent), 'not specified', dat_num$Continent)

dat_climate <- dat_final %>% 
  mutate(
    climate_researcher = as.numeric(research_fact == 'A great deal')
  ) %>% 
  filter(research_fact %in% c('Not at all', 'A great deal'))

behaviors <- list(
  # Civic behaviors
  'talk_climate' = 'Talked about climate with others',
  'donate_money' = 'Donated to climate organizations',
  'signed_petitions' = 'Signed petitions',
  'advocated_change' = 'Advocated change within institution',
  'engaged_policymakers' = 'Engaged with politicians',
  'engaged_disobedience' = 'Engaged in civil disobedience',
  'engaged_protest' = 'Engaged in protest',
  'engaged_advocacy' = 'Engaged in advocacy',
  'wrote_letters' = 'Wrote letters to politicians',
  
  # Lifestyle behaviors
  'reduced_flying' = 'Reduced flying',
  'reduced_car' = 'Reduced car usage',
  'electric_vehicle' = 'Switched to electric vehicle',
  'energy_home' = 'Switched to renewable energy at home',
  'veggie_diet' = 'Follows a mostly vegetarian or vegan diet',
  'fewer_children' = 'Decided to have fewer or no children'
)

behavior_names_map <- unlist(behaviors)
behavior_map <- list(
  'Civic action' = names(behaviors[seq(9)]),
  'Lifestyle change' = names(behaviors[seq(10, 15)])
)
```

# Main analyses
We compute the empirical proportions, used later.
```{r, fig.height = 14}
# Compute empirical proportions, used later
df <- dat_final %>% 
  group_by(Research_std) %>% 
  summarize(across(all_of(names(behaviors)), mean)) %>% 
  mutate(research = factor(
    Research_std, labels = c('Not at all', 'Very little', 'A moderate amount', 'Quite a bit', 'A great deal'))
  ) %>% 
  select(research, everything(), -Research_std) %>% 
  pivot_longer(cols = -research, names_to = 'behavior', values_to = 'value') %>% 
  add_behavior_categories(behavior_map) %>% 
  mutate(behavior = unname(unlist(behaviors[behavior])))
```

## Figure 1: Proportion of actions
```{r}
library(doParallel)
library(marginaleffects)
registerDoParallel(cores = 10)

behavior_list <- names(behaviors)

form <- make_form(
  'talk_climate', random_intercept = FALSE, random_slope = FALSE,
  binarize = TRUE, marginal = TRUE, worry = FALSE, informed = FALSE
)

filename <- '../models/climate_marginal_talk_climate.RDS'

# Run one initial model so below we don't need to recompile them, but can use this one
fit_initial_marginal <- run_model(
  form, filename, dat_climate, use_model = NULL,
  cores = 1, chains = 2, family = bernoulli, force = FALSE, iter = 4000, warmup = 500
)

fit_all_marginal <- foreach(i = seq(length(behaviors))) %dopar% {
  b <- names(behaviors)[i]
  
  filename <- paste0('../models/climate_marginal_', b, '.RDS')
  form <- make_form(
    b, random_intercept = FALSE, random_slope = FALSE, binarize = TRUE,
    marginal = TRUE, worry = FALSE, informed = FALSE
  )
  
  fit <- run_model(
    form, filename, dat_climate, use_model = fit_initial_marginal,
    cores = 1, chains = 2, family = bernoulli, force = FALSE, iter = 4000, warmup = 500
  )
  
  res <- list()
  res[[b]] <- fit
  res
}

df_marginal <- do.call('rbind', lapply(seq(15), function(i) {
  fit <- fit_all_marginal[[i]]
  behavior <- names(fit)
  
  get_effects(fit[[1]], behavior, type = 'marginal')
}))

df_marginal <- df_marginal %>% 
  mutate(behavior = unname(unlist(behaviors[behavior])))

df_prob_marginal <- df %>% 
  filter(research %in% c('Not at all', 'A great deal')) %>% 
  mutate(climate_researcher = ifelse(research == 'A great deal', 1, 0)) %>% 
  left_join(df_marginal, by = c('behavior', 'climate_researcher'))

# Order according to largest multiplicative difference
df_prob_marginal_ord <- df_prob_marginal %>% 
  group_by(behavior) %>% 
  mutate(research_diff = max(estimate) / min(estimate)) %>% 
  ungroup() %>% 
  arrange(research_diff) %>% 
  mutate(behavior = factor(behavior, levels = as.character(unique(behavior))))
```

```{r}
cols <- rev(c('#a50f15', '#08519c'))
p <- ggplot(df_prob_marginal_ord, aes(x = behavior, y = value, group = research, color = research)) +
  geom_bar(
    stat = 'identity', position = position_dodge(width = 0.8),
    width = 0.70, aes(fill = research)
  ) +
  geom_point(
    aes(x = behavior, y = estimate), position = position_dodge(width = 0.80),
    size = 2, show.legend = FALSE, color = 'black'
  ) +
  geom_errorbar(
    aes(ymin = ci_lo, ymax = ci_hi), position = position_dodge(width = 0.80),
    width = 0.40, linewidth = 1, show.legend = FALSE, color = 'black'
  ) +
  geom_point(
    aes(x = behavior, y = estimate), position = position_dodge(width = 0.80),
    size = 1, show.legend = FALSE
  ) +
  geom_errorbar(
    aes(ymin = ci_lo, ymax = ci_hi), position = position_dodge(width = 0.80),
    width = 0.30, linewidth = 0.30,
    show.legend = FALSE
  ) +
  theme_minimal() +
  coord_flip() +
  xlab('') +
  ylab('Percent reported engaging') +
  scale_x_discrete(guide = guide_axis(angle = 0)) +
  scale_color_manual(values = cols) +
  scale_fill_manual(
    values = cols, labels = c('Non-climate researchers (n = 2,257)', 'Climate researchers (n = 1,565)')
  ) +
  scale_y_continuous(
    labels = label_percent(scale = 100), limits = c(0, 1), breaks = seq(0, 1, 0.10)
  ) +  # scale = 1 for proportions
  ggtitle('Climate actions by climate and non-climate researchers') +
  theme(
    legend.position = 'top',
    legend.title = element_blank(),
    panel.grid.minor = element_blank(),
    panel.grid.major.y = element_blank(),
    axis.title.x = element_text(size = 12),
    axis.title.y = element_text(size = 12),
    axis.text.x = element_text(size = 10),
    axis.text.y = element_text(size = 10),
    plot.title = element_text(hjust = .5, size = 14),
    strip.text.x = element_text(size = 9, face = 'bold')
  ) + guides(fill = guide_legend(reverse = TRUE), color = FALSE)

p
ggsave('../figures/Figure1.pdf', p, width = 8, height = 10)
```

# Supplemental analyses
Here we reproduce all figures in the appendix of the paper.

## Figure S1: Adjusting for background and other variables
We fit the models using background variables and then also adding the variable how informed one perceives oneself to be on climate change (worry showed no additional effect). We also run a Bayesian binomial model that models the number of civic and lifestyle actions they engaged in overall.

```{r}
registerDoParallel(cores = 10)

form <- make_form(
  'talk_climate', random_intercept = FALSE, random_slope = FALSE,
  binarize = TRUE, marginal = FALSE, worry = FALSE, informed = FALSE
)

filename <- '../models/climate_background_talk_climate.RDS'

# Run one initial model so below we don't need to recompile them, but can use this one
fit_initial_background <- run_model(
  form, filename, dat_climate, use_model = NULL,
  cores = 1, chains = 2, family = bernoulli, force = FALSE, iter = 4000, warmup = 500
)

# Condition only on background variables
fit_all_background <- foreach(i = seq(length(behaviors))) %dopar% {
  b <- names(behaviors)[i]
  
  filename <- paste0('../models/climate_background_', b, '.RDS')
  form <- make_form(
    b, random_intercept = FALSE, random_slope = FALSE, binarize = TRUE,
    marginal = FALSE, worry = FALSE, informed = FALSE
  )
  
  fit <- run_model(
    form, filename, dat_climate, use_model = fit_initial_background,
    cores = 1, chains = 2, family = bernoulli, force = FALSE, iter = 4000, warmup = 500
  )
  
  res <- list()
  res[[b]] <- fit
  res
}

form <- make_form(
  'talk_climate', random_intercept = FALSE, random_slope = FALSE,
  binarize = TRUE, marginal = FALSE, worry = FALSE, informed = TRUE
)

filename <- '../models/climate_informed_talk_climate.RDS'

# Run one initial model so below we don't need to recompile them, but can use this one
fit_initial_informed <- run_model(
  form, filename, dat_climate, use_model = NULL,
  cores = 1, chains = 2, family = bernoulli, force = FALSE, iter = 4000, warmup = 500
)

# Condition on background variables + informed
fit_all_informed <- foreach(i = seq(length(behaviors))) %dopar% {
  b <- names(behaviors)[i]
  
  filename <- paste0('../models/climate_informed_', b, '.RDS')
  form <- make_form(
    b, random_intercept = FALSE, random_slope = FALSE, binarize = TRUE,
    marginal = FALSE, worry = FALSE, informed = TRUE
  )
  
  fit <- run_model(
    form, filename, dat_climate, use_model = fit_initial_informed,
    cores = 1, chains = 2, family = bernoulli, force = FALSE, iter = 4000, warmup = 500
  )
  
  res <- list()
  res[[b]] <- fit
  res
}
```

We calculate average adjusted differences between climate and non-climate researchers below. In other words, for each combination of predictor variables, we calculate the predicted difference between climate and non-climate researchers. We then average those adjusted predictions. This adjusts the difference between the climate and non-climate researchers for the predictor variables. We do not assume a balanced data set (i.e., all levels of the predictor variables being equally likely), but use the empirical distribution of the predictor variables.

```{r}
library(marginaleffects)

if (!file.exists('../data/comparisons.csv')) {
  comp_m <- get_avg_comparisons(fit_all_marginal, behaviors, type = 'marginal', cores = 8)
  comp_b <- get_avg_comparisons(fit_all_background, behaviors, type = 'background_only', cores = 2)
  comp_c <- get_avg_comparisons(fit_all_informed, behaviors, type = 'conditional_all', cores = 2)
  
  comp_all <- rbind(comp_m, comp_b, comp_c) %>% 
    add_behavior_categories(behavior_map) %>% 
    mutate(
      behavior = behavior_names_map[behavior],
      category = factor(category, levels = c('Civic action', 'Lifestyle change'))
    )
    
  # Order them according to marginal model differences
  order_comp <- comp_all %>% 
    filter(type == 'marginal') %>% 
    arrange(category, desc(estimate))
  
  comp_all$behavior <- factor(comp_all$behavior, levels = rev(order_comp$behavior))
  comp_all$type <- factor(comp_all$type, levels = rev(c('marginal', 'background_only', 'conditional_all')))
  write.csv(comp_all, '../data/comparisons.csv', row.names = FALSE)
} else {
  comp_all <- read.csv('../data/comparisons.csv')
}
```

We model the number of civic and lifestyle actions they engaged in.

```{r}
# Marginal
form_adv_marginal <- 'nr_advocacy_actions | trials(9) ~ climate_researcher'
form_ls_marginal <- 'nr_lifestyle_actions | trials(6) ~ climate_researcher'

background <- paste0(
  ' + Age_std + Political_std + position + field + continent + is_tenured + is_female + is_gender_other'
)

# Background variables
form_adv_background <- paste0(form_adv_marginal, background)
form_ls_background <- paste0(form_ls_marginal, background)

# Informed variables
form_adv_informed <- paste0(form_adv_background, ' + Informed_std')
form_ls_informed <- paste0(form_ls_background, ' + Informed_std')

fit_ls_marginal <- run_model(
  form_ls_marginal, '../models/climate_actions_lifestyle_marginal.RDS',
  dat_climate, force = FALSE, cores = 4, family = binomial
)

fit_adv_marginal <- run_model(
  form_adv_marginal, '../models/climate_actions_civic_marginal.RDS',
  dat_climate, force = FALSE, cores = 4, family = binomial
)

fit_ls_background <- run_model(
  form_ls_background, '../models/climate_actions_lifestyle_background.RDS',
  dat_climate, force = FALSE, cores = 4, family = binomial
)

fit_adv_background <- run_model(
  form_adv_background, '../models/climate_actions_civic_background.RDS',
  dat_climate, force = FALSE, cores = 4, family = binomial
)

fit_ls_informed <- run_model(
  form_ls_informed, '../models/climate_actions_lifestyle_informed.RDS',
  dat_climate, force = FALSE, cores = 4, family = binomial
)

fit_adv_informed <- run_model(
  form_adv_informed, '../models/climate_actions_civic_informed.RDS',
  dat_climate, force = FALSE, cores = 4, family = binomial
)

if (!file.exists('../data/comparisons_binom.csv')) {
  binom_comp <- rbind(
    get_avg_comparisons_binom(fit_ls_marginal, 'Number of lifestyle changes', 'marginal'),
    get_avg_comparisons_binom(fit_ls_background, 'Number of lifestyle changes', 'background_only'),
    get_avg_comparisons_binom(fit_ls_informed, 'Number of lifestyle changes', 'conditional_all'),
    
    get_avg_comparisons_binom(fit_adv_marginal, 'Number of civic actions', 'marginal'),
    get_avg_comparisons_binom(fit_adv_background, 'Number of civic actions', 'background_only'),
    get_avg_comparisons_binom(fit_adv_informed, 'Number of civic actions', 'conditional_all')
  ) %>% 
    mutate(category = rep(c('Lifestyle change', 'Civic action'), each = 3))
  
  write.csv(binom_comp, '../data/comparisons_binom.csv', row.names = FALSE)
} else {
  binom_comp <- read.csv('../data/comparisons_binom.csv')
}
```

```{r}
# Order according to marginal model differences
order_comp <- comp_all %>% 
  filter(type == 'marginal') %>% 
  arrange(category, desc(estimate))

comp_all$behavior <- factor(comp_all$behavior, levels = rev(order_comp$behavior))
comp_all$type <- factor(comp_all$type, levels = rev(c('marginal', 'background_only', 'conditional_all')))
comp_all_combined <- rbind(comp_all, binom_comp)

# Reorder to include the counts
lev <- levels(comp_all$behavior)
lev <- c( 'Number of lifestyle changes', lev[seq(6)], 'Number of civic actions', lev[seq(7, length(lev))])
comp_all_combined$behavior <- factor(comp_all_combined$behavior, levels = lev)

cols <- rev(c('#1F77B4', '#2CA02C', '#FC8D62'))
p <- ggplot(comp_all_combined, aes(x = behavior, y = estimate, color = type, shape = type)) +
  coord_flip() +
  geom_point(
    aes(x = behavior, y = estimate), position = position_dodge(width = 0.75),
    size = 2, show.legend = TRUE
  ) +
  geom_errorbar(
    aes(ymin = ci_lo, ymax = ci_hi), position = position_dodge(width = 0.75),
    width = 0.75, linewidth = 0.80,
    show.legend = TRUE
  ) +
  xlab('') +
  scale_y_continuous(limits = c(0, 14), breaks = seq(0, 14, 1)) +
  ylab('Number of times climate researchers more likely to engage in') +
  theme_minimal() +
  theme(legend.position = 'top') +
  theme_minimal() +
  ggtitle('Multiplicative differences when adjusting for variables') +
  scale_color_manual(
    values = cols,
    labels = c('Background + Informed', 'Background', 'No adjustment')
  ) +
  scale_shape_manual(
    values = c(15, 17, 19),
    labels = c('Background + Informed', 'Background', 'No adjustment')
  ) +
  scale_y_continuous(
    breaks = c(1, 1.25, 1.50, 2, 3, 4, 6, 8, 10, 14), trans = 'log2'
  ) +
  theme(
    legend.position = 'top',
    legend.title = element_blank(),
    panel.grid.minor = element_blank(),
    panel.grid.major.y = element_blank(),
    axis.title.x = element_text(size = 12),
    axis.title.y = element_text(size = 12),
    axis.text.x = element_text(size = 10),
    axis.text.y = element_text(size = 10),
    plot.title = element_text(hjust = .5, size = 14),
    strip.text.x = element_text(size = 9, face = 'bold')
  ) + guides(
    shape = guide_legend(reverse = TRUE, nrow = 1),
    color = guide_legend(reverse = TRUE, nrow = 1)
  )

p

ggsave('../figures/FigureS1.pdf', p, width = 8, height = 10)
```

## Figure S2: Ordinal comparisons
We analyze the extent to which researchers engage in climate actions depending on how related their research is to climate change. We estimate the population proportions and test the hypotheses: (a) all equal, (b) all unequal, (c) increasing proportion with research relatedness to climate. This is used for Figure S2 in the supplement.

```{r, fig.height = 14}
make_tab <- function(varname, dat_final) {
  tab <- t(table(dat_final$Research_std, dat_final[[varname]]))
  colnames(tab) <- c('Not at all', 'Very little', 'A moderate amount', 'Quite a bit', 'A great deal')
  tab
}

compare_models <- function(varname, dat_final) {
  tab <- make_tab(varname, dat_final)
  bf <- contingencyTableBF(tab, sampleType = 'indepMulti', fixedMargin = 'cols')
  post <- posterior(bf, iterations = 10000)
  
  thetas <- cbind(
    post[, 'pi[2,1]'] / (post[, 'pi[2,1]'] + post[, 'pi[1,1]']),
    post[, 'pi[2,2]'] / (post[, 'pi[2,2]'] + post[, 'pi[1,2]']),
    post[, 'pi[2,3]'] / (post[, 'pi[2,3]'] + post[, 'pi[1,3]']),
    post[, 'pi[2,4]'] / (post[, 'pi[2,4]'] + post[, 'pi[1,4]']),
    post[, 'pi[2,5]'] / (post[, 'pi[2,5]'] + post[, 'pi[1,5]'])
  )
  
  # Hr: prop1 < prop2 < prop3 < prop4 < prop5
  ind <- (
    thetas[, 1] < thetas[, 2] &
    thetas[, 2] < thetas[, 3] &
    thetas[, 3] < thetas[, 4] &
    thetas[, 4] < thetas[, 5]
  )
  
  # Posterior samples inline with the restriction versus 
  # prior samples inline with the restriction
  log_bfr1 <- log(mean(ind) / (1 / factorial(5)))
  log_bf10 <- bf@bayesFactor$bf
  log_bfr0 <- log_bfr1 + log_bf10
  
  list(
    'log_bfr1' = log_bfr1, 'log_bf10' = log_bf10, 'log_bfr0' = log_bfr0,
    'tab' = tab, 'thetas' = thetas
  )
}

if (!file.exists('../models/df_models.RDS')) {
  
  bfs <- lapply(names(behaviors), function(behavior) {
    compare_models(behavior, dat_final)
  })
  
  res <- data.frame(
    behavior = rep(names(behaviors), each = 5),
    research = rep(unique(df$research), length(behaviors)),
    log_bf10 = NA,
    log_bfr0 = NA,
    log_bfr1 = NA,
    theta_mean = NA,
    theta_sd = NA,
    theta_q005 = NA,
    theta_q995 = NA,
    theta_ratio = NA,
    theta_ratio_q005 = NA,
    theta_ratio_q995 = NA
  )
  
  for (i in seq(length(behaviors))) {
    m <- bfs[[i]]
    behavior = names(behaviors)[[i]]
    
    res[res$behavior == behavior, ]$log_bf10 <- m$log_bf10
    res[res$behavior == behavior, ]$log_bfr0 <- m$log_bfr0
    res[res$behavior == behavior, ]$log_bfr1 <- m$log_bfr1
    res[res$behavior == behavior, ]$theta_mean <- apply(m$thetas, 2, mean)
    res[res$behavior == behavior, ]$theta_q005 <- apply(m$thetas, 2, function(x) quantile(x, 0.005))
    res[res$behavior == behavior, ]$theta_q995 <- apply(m$thetas, 2, function(x) quantile(x, 0.995))
    res[res$behavior == behavior, ]$theta_sd <- apply(m$thetas, 2, sd)
    
    theta_ratio <- m$thetas[, 5] / m$thetas[, ]
    res[res$behavior == behavior, ]$theta_ratio <- apply(theta_ratio, 2, mean)
    res[res$behavior == behavior, ]$theta_ratio_q005 <- apply(theta_ratio, 2, function(x) quantile(x, 0.005))
    res[res$behavior == behavior, ]$theta_ratio_q995 <- apply(theta_ratio, 2, function(x) quantile(x, 0.995))
  }
  
  df_models <- res %>% 
    add_behavior_categories(behavior_map) %>% 
    filter(category != 'Academic') %>% 
    mutate(category = factor(category, levels = c('Civic action', 'Lifestyle change'))) %>% 
    mutate(behavior = unname(unlist(behaviors[behavior]))) %>% 
    # get difference between min and max
    group_by(behavior) %>% 
    mutate(max_diff = max(theta_mean) - min(theta_mean)) %>% 
    arrange(category, desc(max_diff))
  
  df_models$behavior <- factor(df_models$behavior, levels = as.character(unique(df_models$behavior)))
  saveRDS(df_models, '../models/df_models.RDS')
} else {
  df_models <- readRDS('../models/df_models.RDS')
}

# Combine posterior estimates with empirical proportions
df_models <- df_models %>%
  left_join(
    df %>% select(research, behavior, value),
    by = c('research', 'behavior')
  )

df_models$behavior <- factor(df_models$behavior, levels = as.character(unique(df_models$behavior)))
```


```{r}
df_models$log_bf10_label <- lapply(
  df_models$log_bf10, function(x) as.character(TeX(paste0("$\\log \\, BF_{10}: \\,", round(x, 2), "$")))
)
df_models$log_bfr0_label <- lapply(
  df_models$log_bfr0, function(x) as.character(TeX(paste0("$\\log \\, BF_{r0}: \\,", round(x, 2), "$")))
)

cols <- c('#7570B3', '#1B9E77', '#D95F02')[c(3, 2)]
p <- ggplot(df_models, aes(x = research, y = value, fill = category)) +
  geom_bar(stat = 'identity') +
  geom_point(aes(x = research, y = theta_mean), color = 'black', size = 0.80, show.legend = FALSE) +
  geom_errorbar(
    aes(ymin = theta_q005, ymax = theta_q995), width = 0.10, linewidth = 0.50, color = 'black',
    show.legend = FALSE
  ) +
  geom_text(
    aes(x = 0.50, y = 0.95, label = log_bf10_label),
    color = 'gray60', size = 2.5, parse = TRUE, hjust = 0
  ) +
  geom_text(
    aes(x = 0.50, y = 0.80, label = log_bfr0_label),
    color = 'gray60', size = 2.5, parse = TRUE, hjust = 0
  ) +
  facet_wrap(~ behavior, ncol = 3) +
  theme_minimal() +
  ylab('Percent reported engaging') +
  xlab('Relatedness of research for climate change') +
  scale_x_discrete(guide = guide_axis(angle = 90)) +
  scale_fill_manual(values = cols) +
  scale_y_continuous(labels = label_percent(scale = 100), limits = c(0, 1)) +  # scale = 1 for proportions
  ggtitle('Climate actions across climate change research relatedness') +
  theme(
    legend.position = 'top',
    legend.title = element_blank(),
    panel.grid.minor = element_blank(),
    panel.grid.major = element_blank(),
    axis.title.x = element_text(size = 10),
    axis.title.y = element_text(size = 10),
    axis.text.x = element_text(size = 8),
    axis.text.y = element_text(size = 8),
    plot.title = element_text(hjust = .5, size = 16),
    strip.text.x = element_text(size = 9)
  ) +
  guides(fill = guide_legend('category'))

p
ggsave('../figures/FigureS2.pdf', p, width = 8, height = 10)
```

## Figure S3: Climate action across research fields
Here we show differences between climate researchers in different research fields.

```{r}
# Compute empirical proportions, used later
df_field <- dat_final %>% 
  mutate(
    research = factor(
      Research_std, labels = c('Not at all', 'Very little', 'A moderate amount', 'Quite a bit', 'A great deal')
    )
  ) %>% 
  group_by(research, fieldname) %>% 
  summarize(across(all_of(names(behaviors)), mean)) %>% 
  pivot_longer(cols = c(-research, -fieldname), names_to = 'behavior', values_to = 'value') %>% 
  add_behavior_categories(behavior_map) %>% 
  mutate(behavior = unname(unlist(behaviors[behavior]))) %>% 
  filter(
    research == 'A great deal',
    fieldname %in% c('Natural sciences', 'Social and behavioural sciences', 'Professions and applied sciences')
  )

df_order <- df_field %>% 
  filter(fieldname == 'Social and behavioural sciences') %>% 
  arrange(desc(value))

df_field$behavior <- factor(df_field$behavior, levels = rev(df_order$behavior))
df_field$fieldname <- factor(
  df_field$fieldname,
  levels = rev(c('Social and behavioural sciences', 'Natural sciences', 'Professions and applied sciences'))
)
```

We estimate the proportions again for this set of data, as we did before.
```{r}
dat_field <- dat_final %>% 
   mutate(
    research = factor(
      Research_std, labels = c('Not at all', 'Very little', 'A moderate amount', 'Quite a bit', 'A great deal')
    )
  ) %>% 
  filter(
    research == 'A great deal',
    fieldname %in% c('Social and behavioural sciences', 'Natural sciences', 'Professions and applied sciences')
  )

make_tab <- function(varname, dat_final) {
  tab <- t(table(dat_final$fieldname, dat_final[[varname]]))
  tab
}

compare_models <- function(varname, dat_final) {
  tab <- make_tab(varname, dat_final)
  bf <- contingencyTableBF(tab, sampleType = 'indepMulti', fixedMargin = 'cols')
  log_bf10 <- bf@bayesFactor$bf
  post <- posterior(bf, iterations = 10000)
  
  thetas <- cbind(
    post[, 'pi[2,1]'] / (post[, 'pi[2,1]'] + post[, 'pi[1,1]']),
    post[, 'pi[2,2]'] / (post[, 'pi[2,2]'] + post[, 'pi[1,2]']),
    post[, 'pi[2,3]'] / (post[, 'pi[2,3]'] + post[, 'pi[1,3]'])
  )
  
  list(
    'log_bf10' = log_bf10, 'thetas' = thetas
  )
}

if (!file.exists('../models/df_models_field.RDS')) {
  
  bfs <- lapply(names(behaviors), function(behavior) {
    compare_models(behavior, dat_field)
  })
  
  res <- data.frame(
    behavior = rep(names(behaviors), each = 3),
    fieldname = rep(unique(dat_field$fieldname), length(behaviors)),
    log_bf10 = NA,
    theta_mean = NA,
    theta_sd = NA,
    theta_q005 = NA,
    theta_q995 = NA,
    theta_ratio = NA,
    theta_ratio_q005 = NA,
    theta_ratio_q995 = NA
  )
  
  for (i in seq(length(behaviors))) {
    m <- bfs[[i]]
    behavior <- names(behaviors)[[i]]
    
    res[res$behavior == behavior, ]$log_bf10 <- m$log_bf10
    res[res$behavior == behavior, ]$theta_mean <- apply(m$thetas, 2, mean)
    res[res$behavior == behavior, ]$theta_q005 <- apply(m$thetas, 2, function(x) quantile(x, 0.005))
    res[res$behavior == behavior, ]$theta_q995 <- apply(m$thetas, 2, function(x) quantile(x, 0.995))
    res[res$behavior == behavior, ]$theta_sd <- apply(m$thetas, 2, sd)
    
    theta_ratio <- m$thetas[, 3] / m$thetas[, ]
    res[res$behavior == behavior, ]$theta_ratio <- apply(theta_ratio, 2, mean)
    res[res$behavior == behavior, ]$theta_ratio_q005 <- apply(theta_ratio, 2, function(x) quantile(x, 0.005))
    res[res$behavior == behavior, ]$theta_ratio_q995 <- apply(theta_ratio, 2, function(x) quantile(x, 0.995))
  }
  
  df_models_field <- res %>% 
    add_behavior_categories(behavior_map) %>% 
    filter(category != 'Academic') %>% 
    mutate(category = factor(category, levels = c('Civic action', 'Lifestyle change'))) %>% 
    mutate(behavior = unname(unlist(behaviors[behavior]))) %>% 
    arrange(category, desc(theta_mean))
  
  df_order <- df_models_field %>% 
    filter(fieldname == 'Social and behavioural sciences') %>% 
    arrange(desc(theta_mean))
  
  df_models_field$behavior <- factor(
    df_models_field$behavior, levels = rev(as.character(unique(df_order$behavior)))
  )
  df_models_field$fieldname <- factor(
    df_models_field$fieldname,
    levels = rev(c('Social and behavioural sciences', 'Natural sciences', 'Professions and applied sciences'))
  )
  saveRDS(df_models_field, '../models/df_models_field.RDS')
} else {
  df_models_field <- readRDS('../models/df_models_field.RDS')
}

# Combine posterior estimates with empirical proportions
df_models_field <- df_models_field %>%
  left_join(
    df_field %>% select(fieldname, behavior, value),
    by = c('fieldname', 'behavior')
  )
```

```{r}
cols <- rev(c('#1F77B4', '#2CA02C', '#FC8D62'))
p <- ggplot(df_models_field, aes(x = behavior, y = value, fill = fieldname, color = fieldname)) +
  geom_bar(
    stat = 'identity', position = position_dodge(width = 0.8),
    width = 0.70, aes(fill = fieldname)
  ) +
  geom_point(
    aes(x = behavior, y = theta_mean), position = position_dodge(width = 0.80),
    size = 2, show.legend = FALSE, color = 'black'
  ) +
  geom_errorbar(
    aes(ymin = theta_q005, ymax = theta_q995), position = position_dodge(width = 0.80),
    width = 0.40, linewidth = 1, show.legend = FALSE, color = 'black'
  ) +
  geom_point(
    aes(x = behavior, y = theta_mean), position = position_dodge(width = 0.80),
    size = 1, show.legend = FALSE
  ) +
  geom_errorbar(
    aes(ymin = theta_q005, ymax = theta_q995), position = position_dodge(width = 0.80),
    width = 0.30, linewidth = 0.30,
    show.legend = FALSE
  ) +
  theme_minimal() +
  coord_flip() +
  xlab('') +
  ylab('Percent reported engaging') +
  scale_x_discrete(guide = guide_axis(angle = 0)) +
  scale_color_manual(values = cols) +
  scale_fill_manual(
    values = cols,
    labels = rev(
      c('Social and behavioural sciences (n = 341)',
        'Natural sciences (n = 716)',
        'Professions and applied sciences (n = 392)')
    )
  ) +
  scale_y_continuous(
    labels = label_percent(scale = 100), limits = c(0, 1), breaks = seq(0, 1, 0.10)
  ) +  # scale = 1 for proportions
  ggtitle('Climate actions by climate researchers in different fields') +
  theme(
    legend.position = 'top',
    legend.title = element_blank(),
    panel.grid.minor = element_blank(),
    panel.grid.major.y = element_blank(),
    axis.title.x = element_text(size = 12),
    axis.title.y = element_text(size = 12),
    axis.text.x = element_text(size = 10),
    axis.text.y = element_text(size = 10),
    plot.title = element_text(hjust = .5, size = 14),
    strip.text.x = element_text(size = 9, face = 'bold')
  ) + guides(fill = guide_legend(reverse = TRUE, nrow = 3), color = FALSE)

p
ggsave('../figures/FigureS3.pdf', p, width = 8, height = 10)
```


## Figure S4: Correlation between actions
We compute correlations between all actions (as well as self-reported carbon-intensity of lifestyle and political orientation).

```{r}
library(corrplot)
library(doParallel)
registerDoParallel(cores = 8)

varnames <- c(names(behavior_names_map), 'Lifestyle_std', 'Political_std')
dat_cor <- dat_final %>% select(varnames)

p <- length(varnames)
corr_all <- get_cors(dat_cor, '../models/action_correlations_all.RDS')
```

```{r, fig.width = 14, fig.height = 14}
varmap <- c(
  behavior_names_map,
  'Lifestyle_std' = 'Carbon-intensity of lifestyle',
  'Political_std' = 'Political orientation'
)

cor_mat <- corr_all$cor_mat
rownames(cor_mat) <- colnames(cor_mat) <- varmap[colnames(cor_mat)]
diag(cor_mat) <- 0

# Reorient like the other figures
cor_order <- c(levels(df_models$behavior), 'Carbon-intensity of lifestyle', 'Political orientation')
cor_mat <- cor_mat[cor_order, cor_order]
diag(cor_mat) <- NA

pdf('../figures/FigureS4.pdf', width = 8, height = 8)
corrplot(
  cor_mat, method = 'color', type = 'upper', number.cex = 0.60,
  addCoef.col = 'black',
  tl.cex = 0.80, addrect = 20, tl.col = 'black',
  na.label = ' '
)
dev.off()
```

```{r}
corrplot(
  cor_mat, method = 'color', type = 'upper', number.cex = 0.60,
  addCoef.col = 'black',
  tl.cex = 0.80, addrect = 20, tl.col = 'black',
  na.label = ' '
)
```

## Table S1 & S2: Descriptive statistics
Here we show descriptive statistics of a number of background variables.

```{r}
age_labels <- c('18 - 24 years', '25-34 years', '35-44 years', '45-54 years', '55-64 years', '65+ years')
gender_labels <- c('Male', 'Female', 'Non-binary', 'Prefer to self-describe', 'Prefer not to say')
field_labels <- c(
  'Social and behavioural sciences', 'Natural sciences', 'Medical sciences',
  'Professions and applied sciences', 'Formal sciences', 'Humanities', 'Other'
)
position_labels <- c(
  'PhD candidate', 'Postdoc', 'Assisstant professor',
  'Associate professor', 'Full professor',
  'Scientist or researcher in industry',
  'Scientist or researcher at a public research institute',
  'Scientist or researcher at a non-profit organization',
  'Other'
)
political_labels <- c('1', '2', '3', '4', '5', '6', '7')
carbon_labels <- c('Much lower', 'Lower', 'About the same', 'Higher', 'Much higher')
continent_labels <- c('Europe', 'North America', 'South America', 'Asia', 'Africa', 'Oceania')

dat_descr <- dat_num %>% 
  filter(Research %in% c(1, 5)) %>% 
  mutate(
    Age = factor(Age, labels = age_labels),
    Gender = factor(Gender, labels = gender_labels),
    fieldname = factor(fieldname, levels = field_labels),
    Position = factor(Position, labels = position_labels),
    Political = factor(Political, labels = political_labels),
    Research = factor(Research, labels = c('Non-climate researchers', 'Climate researchers')),
    Continent = factor(Continent, levels = continent_labels),
    Lifestyle = factor(Lifestyle, labels = carbon_labels)
  )

dat_age <- dat_descr %>% 
  group_by(Research, Age) %>% 
  summarize(n_age = n()) %>% 
  group_by(Research) %>% 
  mutate(prop_age = 100 * round(n_age / sum(n_age), 2)) %>% 
  mutate(final_age = paste0(n_age, ' (', prop_age, '%)')) %>% 
  select(Research, Age, final_age)

dat_gender <- dat_descr %>% 
  group_by(Research, Gender) %>% 
  summarize(n_gender = n()) %>% 
  group_by(Research) %>% 
  mutate(prop_gender = 100 * round(n_gender / sum(n_gender), 2)) %>% 
  mutate(final_gender = paste0(n_gender, ' (', prop_gender, '%)')) %>% 
  select(Research, Gender, final_gender)

dat_field <- dat_descr %>% 
  select(-Field) %>% 
  rename(Field = fieldname) %>% 
  group_by(Research, Field) %>% 
  summarize(n_field = n()) %>% 
  group_by(Research) %>% 
  mutate(prop_field = 100 * round(n_field / sum(n_field), 2)) %>% 
  mutate(final_field = paste0(n_field, ' (', prop_field, '%)')) %>% 
  select(Research, Field, final_field)

dat_pos <- dat_descr %>% 
  group_by(Research, Position) %>% 
  summarize(n_pos = n()) %>% 
  group_by(Research) %>% 
  mutate(prop_pos = 100 * round(n_pos / sum(n_pos), 2)) %>% 
  mutate(final_pos = paste0(n_pos, ' (', prop_pos, '%)')) %>% 
  select(Research, Position, final_pos)

dat_pol <- dat_descr %>% 
  group_by(Research, Political) %>% 
  summarize(n_pol = n()) %>% 
  group_by(Research) %>% 
  mutate(prop_pol = 100 * round(n_pol / sum(n_pol), 2)) %>% 
  mutate(final_pol = paste0(n_pol, ' (', prop_pol, '%)')) %>% 
  select(Research, Political, final_pol)

dat_cont <- dat_descr %>% 
  group_by(Research, Continent) %>% 
  summarize(n_cont = n()) %>% 
  group_by(Research) %>% 
  mutate(prop_cont = 100 * round(n_cont / sum(n_cont), 2)) %>% 
  mutate(final_cont = paste0(n_cont, ' (', prop_cont, '%)')) %>% 
  select(Research, Continent, final_cont)

dat_ls <- dat_descr %>% 
  group_by(Research, Lifestyle) %>% 
  summarize(n_ls = n()) %>% 
  group_by(Research) %>% 
  mutate(prop_ls = 100 * round(n_ls / sum(n_ls), 2)) %>% 
  mutate(final_ls = paste0(n_ls, ' (', prop_ls, '%)')) %>% 
  select(Research, Lifestyle, final_ls)

prep <- function(df, value) {
  df <- df %>% 
    spread(key = 'Research', value = value)
  varname <- colnames(df)[1]
  df$Variable <- varname
  colnames(df) <- c('Variablename', colnames(df)[-1])
  df %>% 
    select(Variable, Variablename, everything())
}

df_all <- bind_rows(
  prep(dat_age, 'final_age'),
  prep(dat_gender, 'final_gender'),
  prep(dat_cont, 'final_cont'),
  prep(dat_field, 'final_field'),
  prep(dat_pos, 'final_pos'),
  prep(dat_pol, 'final_pol'),
  prep(dat_ls, 'final_ls')
)

kable_df <- kable(df_all, format = 'latex', booktabs = TRUE)
print(kable_df)
```

# Session info
```{r}
sessionInfo()
```
